---
title: "Food Explorer (Exercises to practice)"
output:
  html_document:
    toc: yes
date: "2023-05-14"
---

```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
``` 

```{r import_csv}
food_data <- read.csv("data/foodData.csv")
```

# 1. Which category of food has the highest average price?
```{r exercise1}

# group_by on "Category" and calculate average
group_categories <- food_data %>% 
                    group_by(Category) %>%
                    summarise(average = mean(Price))

# Sort by the highest mean price and get the first record
max_mean_price_category <- group_categories %>%
  arrange(desc(average)) %>%
  slice_head(n = 1)

max_mean_price_category
```

# 2. What is the most common country of origin for the food items?
```{r exercise2}
group_country <- food_data %>%
                 group_by(Country.of.Origin)  %>%
                  summarise(count = n())
                  
most_common_country_of_origin <- group_country %>%
                                  arrange(desc(count)) %>%
                                  slice_head(n = 1)

most_common_country_of_origin
```

# 3. Calculate the average calories per serving for the food items in the "Salad" category.
```{r exercise3}
food_data %>%
  filter(Category == "Salad") %>%
  summarise(salad_average_calories_per_serving = mean(Calories.per.Serving)) 
```

# 4. How many food items have a protein content greater than 20 grams?
```{r exercise4}
high_protein_items <- food_data %>%
                      filter(Protein..g. > 20)

nrow(high_protein_items)
```

That are:
`r high_protein_items %>% kable()`

# 5. Determine the distribution of carbohydrate content for the food items.
```{r exercise5}
distribution <- food_data %>%
                arrange(Carbohydrate..g.) %>%
                summarise(maximum = max(Carbohydrate..g.),
                          minimum = min(Carbohydrate..g.),
                          mean = mean(Carbohydrate..g.),
                          median = median(Carbohydrate..g.),
                          'standard deviation' = sd(Carbohydrate..g.))

distribution %>% kable()

hist(food_data$Carbohydrate..g., 
     breaks = "Sturges",  # Specify the number of bins or choose a binning method
     main = "Carbohydrate Content Distribution",  # Title of the plot
     xlab = "Carbohydrate (g)",  # Label for x-axis
     ylab = "Frequency",  # Label for y-axis
     col = "lightblue"  # Color of the bars
)
```

# 6. What is the average fat content of the food items in the "Pasta" category?
```{r exercise6}
food_data %>%
  filter(Category == "Pasta") %>%
  summarise(pasta_fat_average_content = mean(Fat..g.))
```







